---
title: "A fast-track-publishing demo"
output: 
  Gmisc::ftp_document:
    fig_caption: TRUE
---

End section of methods
======================

```{r Data_prep, echo=FALSE, message=FALSE, warning=FALSE}
# Moved this outside the document for easy of reading
# I often have those sections in here
source("Setup_and_munge.R")
```

```{r Versions}
info <- sessionInfo()
r_ver <- paste(info$R.version$major, info$R.version$minor, sep=".")
```

All analyses were performed using R (ver. `r r_ver`)[R Core Team, 2013] and packages rms (ver. `r info$otherPkgs$rms$Version`) [F. Harrell, 2014] for analysis, Gmisc for plot and table output (ver. `r info$otherPkgs$Gmisc$Version`), and knitr (ver `r info$otherPkgs$knitr$Version`) [Xie, 2013] for reproducible research.

Results
=======

We found `r nrow(melanoma)` patients with malignant melanoma between the years `r paste(range(melanoma$year), collapse=" and ")`. Patients were followed until the end of 1977, the median follow-up time was `r sprintf("%.1f", median(melanoma$time_years))` years (range `r paste(sprintf("%.1f", range(melanoma$time_years)), collapse=" to ")` years). Males were more common than females and had also a higher mortality rate.

```{r Table1, results='asis', cache=FALSE}
table_data <- list()
getT1Stat <- function(varname, digits=0){
  getDescriptionStatsBy(melanoma[, varname], melanoma$status, 
                        add_total_col=TRUE,
                        show_all_values=TRUE, 
                        hrzl_prop=TRUE,
                        statistics=FALSE, 
                        html=TRUE, 
                        digits=digits)
}

# Get the basic stats
table_data[["Sex"]] <- getT1Stat("sex")
table_data[["Age<sup>&dagger;</sup>"]] <- getT1Stat("age")
table_data[["Ulceration"]] <- getT1Stat("ulcer")
table_data[["Thickness<sup>&Dagger;</sup>"]] <- getT1Stat("thickness", digits=1)

# Now merge everything into a matrix
# and create the rgroup & n.rgroup variabels
rgroup <- c()
n.rgroup <- c()
output_data <- NULL
for (varlabel in names(table_data)){
  output_data <- rbind(output_data, table_data[[varlabel]])
  rgroup <- c(rgroup, varlabel)
  n.rgroup <- c(n.rgroup, nrow(table_data[[varlabel]]))
}

# Add a column spanner for the death columns
cgroup <- c("", "Death")
n.cgroup <- c(2, 2)
colnames(output_data) <- gsub("[ ]*death", "", colnames(output_data))

htmlTable(output_data, align="rrrr",
          rgroup=rgroup, n.rgroup=n.rgroup, 
          rgroupCSSseparator="", 
          cgroup = cgroup,
          n.cgroup = n.cgroup,
          rowlabel="", 
          caption="Baseline characteristics", 
          tfoot="<sup>&dagger;</sup> Age at the time of surgery. <br/><sup>&Dagger;</sup> Tumour thicknes, also known as Breslow thickness, measured in mm.", 
          ctable=TRUE)
```

Main results
------------

```{r C_and_A, results='asis'}
label(melanoma$sex) <- "Sex"
label(melanoma$age) <- "Age"
label(melanoma$ulcer) <- "Ulceration"
label(melanoma$thickness) <- "Breslow thickness"

# Setup needed for the rms coxph wrapper
ddist <- datadist(melanoma)
options(datadist = "ddist")

# Do the cox regression model 
# for melanoma specific death
msurv <- Surv(melanoma$time_years, melanoma$status=="Melanoma death")
fit <- cph(msurv ~ sex + age + ulcer + thickness, data=melanoma)

# Print the model
printCrudeAndAdjustedModel(fit, desc_digits=0,
                           caption="Adjusted and unadjusted estimates for melanoma specific death.",
                           desc_column=TRUE,
                           add_references=TRUE, 
                           ctable=TRUE)

pvalues <- 
  1 - pchisq(coef(fit)^2/diag(vcov(fit)), df=1)
```

After adjusting for the three variables, age, sex, tumor thickness and ulceration, only the latter two remained significant (p-value `r pvalueFormatter(pvalues["ulcer=Present"], sig.limit=10^-3)` and `r pvalueFormatter(pvalues["thickness"], sig.limit=10^-3)`), see table `r as.numeric(options("table_counter"))-1` and figure I.

```{r Regression_forestplot, fig.height=3, fig.width=5, dpi=300, fig.cap="A forest plot comparing the regression coefficients."}
# I've adjusted the coefficient for age to be by 
forestplotRegrObj(update(fit, .~.-age+I(age/10)), 
                  order.regexps=c("Female", "age", "ulc", "thi"),
                  box.default.size=.25, xlog=TRUE,
                  new_page=TRUE, clip=c(.5, 6), rowname.fn=function(x){
  if (grepl("Female", x))
    return("Female")
  
  if (grepl("Present", x))
    return("Ulceration")
  
  if (grepl("age", x))
    return("Age/10 years")

  return(capitalize(x))
})
```
